---
title: "`r read.dcf('DESCRIPTION', fields = 'Package')[1]`"  
author: "`r rworkflows::use_badges()`" 
date: "<h4>README updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  github_document
---

<!-- To modify Package/Title/Description/Authors fields, edit the DESCRIPTION file -->

```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("DESCRIPTION", fields = "Package")[1]
title <- read.dcf("DESCRIPTION", fields = "Title")[1]
description <- gsub("\n"," ",read.dcf("DESCRIPTION", fields = "Description")[1])
URL <- read.dcf('DESCRIPTION', fields = 'URL')[1]
owner <- strsplit(URL,"/")[[1]][4]
repo <-strsplit(URL,"/")[[1]][5]
```
 
## Introduction

The MSTExplorer package is an extension of the
[EWCE](https://nathanskene.github.io/EWCE/articles/EWCE.html) package. It is
designed to run expression weighted celltype enrichment (EWCE) on multiple gene
lists in parallel. The results are then stored both as separate .rds files, one
for each  individual EWCE analysis, as well as a in a single dataframe
containing all the results. This package is useful in cases where you have a
large number of related, but separate, gene lists.

## Installation 

Within R: 

```R
if(!require("remotes")) install.packages("remotes")

remotes::install_github("`r paste(owner,repo,sep='/')`")
library(`r pkg`)
```

## Documentation 

#### [Website](https://`r owner`.github.io/`r pkg`) 
#### [Get started](https://`r owner`.github.io/`r pkg`/articles/`r pkg`)
#### [Docker/Singularity Container](https://`r owner`.github.io/`r pkg`/articles/docker.html)

## Citation

If you use ``r pkg``, please cite: 

<!-- Modify this by editing the file: inst/CITATION  -->
> `r utils::citation(pkg)$textVersion`

## Contact

### [Neurogenomics Lab](https://www.neurogenomics.co.uk)   
UK Dementia Research Institute  
Department of Brain Sciences  
Faculty of Medicine  
Imperial College London  
[GitHub](https://github.com/neurogenomics)

## Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  
<hr>
