---
title: "hexSticker"
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{hexSticker}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE, include=TRUE}
#### Install deps ####
for(p in c("hexSticker","dplyr","here")){
    if(!require(p,character.only = TRUE)) install.packages(p)     
}
#### Get package metadata deps ####
pkg <- read.dcf(here::here("DESCRIPTION"), fields = "Package")[1]
description <- read.dcf(here::here("DESCRIPTION"), fields = "Description")[1]
```

# Create hex sticker

Hex stickers are a great way to give your R package its very own logo. 
See [here for some examples](http://hexb.in/) from other packages. 

Here are some R packages that you may find helpful for making hex stickers:

## [`hexSticker`](https://github.com/GuangchuangYu/hexSticker)  
Helper functions for creating reproducible hexagon sticker purely in R.

## [`ggimage`](https://github.com/GuangchuangYu/ggimage) 
Supports image files and graphic objects to be visualized in `ggplot2` graphic system.

## [`ggpattern`](https://coolbutuseless.github.io/package/ggpattern/)
Custom `ggplot2` geoms which support filled areas with geometric and image-based patterns.

## [`magick`](https://cran.r-project.org/web/packages/magick/vignettes/intro.html)
Advanced Image-Processing in R.

## [`aRtsy`](https://github.com/koenderks/aRtsy)
R package for making generative art using `ggplot2`.

## [`threed`](https://github.com/coolbutuseless/threed)
Three-Dimensional Object Transformations.

## Create file path

Create file path to save hex sticker to.

```{r}
filename <- here::here("inst","hex","hex.png")
dir.create(dirname(filename), showWarnings = FALSE, recursive = TRUE)
```

## Make sticker 

```{r}    
s_size = 1
stick <- hexSticker::sticker( 
  subplot = here::here("inst/hex/2BIeTx6RN6O00CAaeY68q2.jpg"),
  #### Package name ####
  package = paste(strsplit(pkg,"")[[1]],collapse = " "), 
  p_size=18, p_y = 1.3, p_color = ggplot2::alpha("white",.9),
  #### Subplot #####
  s_x=1, s_y=1,  s_height = s_size, s_width = s_size,
  #### Fill & border ####
  h_fill = "white", h_color = ggplot2::alpha("white",.55), h_size = 2,
  #### Spotlight ####
  spotlight = TRUE, l_alpha = .3, l_width = 10, l_x = .5, l_y = .75,
  #### File output ####
  dpi = 300, filename = filename,white_around_sticker = T)
print(stick)
```

# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  
